Generate data for NOBA cod ensemble modeling

### 2020-03-19 NOBAcod.Rmd
formatting
NOBA cod working with age class wrappers

*Special note: Atlantis output files usually have the prefix "output" and `atlantisom` expects this. NOBA output files use a different naming convention. I've appended "output" to the beginning of each NOBA output filename for `atlantisom` to work.*

@@

@@

### Write input data for specific assessment models

>>>>

**Special note:** *Atlantis output files usually have the prefix "output" and `atlantisom` expects this. NOBA output files use a different naming convention. I've appended "output" to the beginning of each NOBA output filename for `atlantisom` to work. Need to update `atlantisom` functions for user-specified output filenames.*

**Special note 2:** *NOBA's nordic_groups_v04.csv file has an inFishery column, rather than the `atlantisom` expected InFishery column. I've changed the column name in the input file, but need to add robustness to atlantisom code to remove case sensitivity.*

### Config files

@@

### Using the wrappers

@@

### Wrapper test results {.tabset}

#### Biomass index
```{r bioind-1}

library(ggthemes)
omlist_ss <- NOBAom_cod
source(here("config/omdimensions.R"))

#read time series data
survObsBiom <- readRDS(file.path(d.name, paste0(scenario.name, "surveyB.rds")))

survObsBiom <- survObsBiom[[1]]

plotB <-ggplot() +
  geom_line(data=survObsBiom, aes(x=time/stepperyr,y=atoutput, color="survey Biomass"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free")

#### Catch time series
```{r catchind-1}
#read time series data
catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))

catchbio_ss <- catchbio_ss[[1]]

plotC <-ggplot() +
  geom_line(data=catchbio_ss, aes(x=time/365,y=atoutput, color="observed Catch"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotC +
  facet_wrap(~species, scales="free")

#### Survey length composition
```{r lencomp-1}

#add this to om_indices function so that this has years when read in
fish_len_comp_data$time <- as.integer(floor(fish_len_comp_data$time/fstepperyr))

len <- filter(len_comp_data, time %in% c(55:175))

  lfplot <- ggplot(len, aes(upper.bins)) +
    geom_bar(aes(weight = atoutput)) +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          len$species))

  lfplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")

#### Age composition (age classes)
```{r agecomp-1}

#add this to om_indices function so that this has years when read in
fish_age_comp$time <- as.integer(floor(fish_age_comp$time/fstepperyr))

Natageplot <- ggplot(Natagesubsp, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          sp))

  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 1, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 2, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 3, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 4, scales="free")
```

### {-}

Wrappers work for NOBA cod using standard age classes. Now to modify the underlying code to get full age structure.

## Updating functions for full age structure

## Write input data for specific assessment models
